\title{Uncle Tom's Cabin}
\author{Harriet Beecher Stowe}
\date{1852}
\pdfbookmark{Title Page}{title}
\begin{titlepage}
    \begin{center}
        \vspace*{1in}
        {\Huge Uncle Tom's Cabin;\par}
        {\large Or Negro Life in The Slave\\ States Of America.\par}
        {\large by\par}
        {\huge Harriet Beecher Stowe.---1852}
        \vfill
        {\large Reprinted by\\ Robert R. Russell---2023}
    \end{center}
\end{titlepage}

\cleardoublepage{}

\tableofcontents

%\chapter{Comments from the reprinter}

%Keeping the preface to this edition is troubling me. By the fifth paragraph the
%preface has become almost sickeningly moralistic in my view.

%My viewpoint is affected by the nearly 171 years from 1852 to 2023 when I write
%this. 

\chapter{Preface.}

Good books, like good actions, best explain themselves; they most effectively
storm both heart and head, their virtues drape them with greatest dignity, the
less they are cumbered by eulogistic comment. But while, therefore, we may be
content with merely introducing this good book to British readers, leaving them
to discover what beauties and excellences, what tenderness, and humour, and
delicate pencillings have rendered the story so popular in the free states of
America---the purpose of the book we ourselves have some property in, and in
reprinting it must assert the claim; for the purpose is to disabuse large
communities of mankind of the belief that the Lord our God, when He gave
dominion to man ``over the fish of the sea, and over the fowl of the air, and
over the cattle,'' bestowed this dominion only on prospective races of a certain
colour, and included under the designation ``cattle'' other prospective races of
another colour.

Were this, however, \emph{only} a belief pitiful and blasphemous as it is, the
full luxury of its enjoyment might be allowed to those who hold it; leaving
them to defend the creed in the face of Our Father, one day, while the avenging
angel, with his flaming sword, shall turn the leave of Holy Writ. But since this
belief is acted upon---since the dominion of mankind over man \emph{is}
established through violence and theft, and maintained by knotted thongs,
hissing branding-irons, rifles, dogs, and the laws of glorious republics, it is
another thing. This is \emph{our} business also, as well as of Him who drowned
the might of Egypt at the feet of its slaves. It is incumbent upon ever honest
man---it is incumbent upon every fettered thief, so he have respect for a single
virtue of detestation of a solitary vice---to aid in shaming down the man-trade;
for it is scarcely possible to name a crime from murder downward that it does
not prolifically gender.

To have been foremost in acknowledging the evils inflicted in the traffic, the
first atone for its guilt and to force some measure of redress from other
nations, England may justly claim credit for; the fact that to stand once within
the boundaries of British rule is to place the artillery of an empire betwixt
any man and slavery, advances that empire, all burdened and heavy ladened as it
is, to a degree of national excellence unattained elsewhere either in old times
or in new. But when Wilberforce preached and Broughman thundered, it was not
only that the disgrace of such oppression be removed from \emph{us}, but that
the pains of such oppression should be removed from all mankind. It was not to
whitewash the national dignity, but to reclaim a degraded race from degradation,
that so mighty efforts were made by a generation now almost past. If, then, this
spirit be still in us, we shall cease to regard our efforts in this direction as
accomplished; and though we have not power further to enforce obedience to the
laws of humanity by which all nations are brought equally under the government
of God, and of which every man is an officer, and though appeals to the sense
and feeling of American slave-owners and slave-breeders have hitherto fallen
short of the mark, and got drowned in their breeches pocket, the moral influence
of all free nations is still a debt due to their victims.

Mainly through such consideration has the present edition of ``Uncle Tom's
Cabin'' become published. We believe---it is already evident, in fact---that the
dissemination of this work throughout America will effect what ``La Picciola''
elsewhere effected and tyranny less complete and vile. It will sap the
foundations of an institution which has prospered amid tempests of indignant
eloquence; and we prophesy that what has been denied to Justice, contrary to the
lowest instincts of brute compassion, will now be resigned, bit by bit, at the
shrine of Respectability. Wherever the book is read---and thousands of copies
are already quietly at work in thousands of homes---contempt for the upholders
of slavery must follow. Now contempt, unlike indignation, is a weapon impossible
to parry; it loses little of its force by being struck from a distance; and, in
a good cause, spreads like contagion. Therefore the sooner the story is
circulated in every colony and village where English can be read, the sooner
must the dread realities it chronicles become mere traditions to wonder over.

Until, however, this consummation be effected in so far as she is criminal, it
is vain to assert for the republic of the United States greatness, of any share
in the progress of the world. Commercial greatness we are willing to allow her;
but prosperous infamy is not palliated infamy, and cruelty imbibes no virtue
from purple and fine linen. It may or may not be great to be powerful and rich,
according as the question is approached from earth or heaven; but when increase
grows from tears and blood, when power is subserved by crushing into the hearts
of thousands all those feelings and impulses by which men are known to be the
children of an Almighty Father---to prove \emph{that} greatness we must view it
neither from earth nor heaven. Nor is the world progressed by destroying in
certain races both the power and the motive for advancement---by depriving them
even of their right to their children, and their wives and daughters of the
right of being virtuous---by heaping upon them such indignities that they
themselves resign all pretensions to manhood and immortal life, and are content
to live and die like horned beast in the stall. Let the slave-breeder and
slave-holder reflect upon this last consideration. There is surely something
frightfully responsible in thus standing between God and the souls of men---in
rendering these souls lies to the their possessors; surely there is some danger
in treading out that image of Himself which God has impressed upon the heart of
every woman and man. In view of such enormity, even to barter the bodies of
living men is a venial offence; but as this fearful sin against Heaven grows out
of the smaller sin against humanity, it becomes obligatory upon us a
thousand-fold to use whatever means are at hand to destroy altogether the curse
of slavery. Regarding it, however, simply as a sin against humanity, it is
sufficiently terrible to excuse destruction, spite of \emph{vested interest}.
``Tell me not of rights,'' said Lord Brougham, ``talk not of the property of the
planter in his slaves. I deny the right, I acknowledge not the property. The
principles, the feeling of our common nature rise in rebellion against it. Be
the appeal made to the understanding or the heart, the sentence is the same that
rejects it. In vain you tell me of laws which sanction such a claim. There is a
law above all the enactments of human codes, the same throughout the world, the
same in all times, such as it was before the daring genius of Columbus pierced
the night of ages, and opened to one world the sources of power, wealth, and
knowledge---to another unutterable woes, such as it is at this day. It is the
law written by the finger of God upon the heart of man; and by that law,
unchangable and eternal, while men despise fraud, and loathe rapine, and abhor
blood, they will reject with indignation the wild and guilty phantasy that man
can hold property in man.''

It is unnecessary to add another word. We commit the volume into the hands of
the public, trusting that by such gentle means as it embodies an iniquity so
gigantic and terrible will speedily be done away, and the statute-books of
America purged of those leaves which render her laws contradiction and
absurdity. If, however, the slave-states continue to resist the wholesome
influences thus mercifully arrayed against their staple traffic, and still
persist in wickedness, we need only turn to history and Holy Writ to understand
the results. Not always shall Loving-kindness plead with Cain. Not always shall
the blood of lashed and murdered men reek at the gates of Heaven---the cries of
bereaved mothers, of bereaved children, ring around the throne; nor will He
always await the return of the oppressor to justice. For in Eastern deserts the
ruins of past nations, whitening like skeletons in the sun, declare that,
surrounded as we are by mercy, there yet stands upon the verge of heaven an
avenging angel armed to destroy that whose gates are barred against justice and
humanity.
\begin{flushright}
G.
\end{flushright}
